\bf Title here

### 2020-05-31 paper/paper.tex
add noisy index function section; add polish alpha for search_goedesic section

Guided tour is usually used in conjunction projection pursuit, a method
coined by \citet{friedman1974projection} to detect ``interesting''
low-diemsion projection of multivariate data. A projection pursuit
requires the definition of a projection pursuit index function and an
optimisation routine. The projection pursuit index measures the
``interestingness'' of data defined as its departure from normality.
Numerous indices have been proposed in the literature, including
lengendre index \citep{friedman1974projection}, hermite index
\citep{hall1989polynomial}, natural hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}. An optimisation routine is required to
find the projection basis (thus projection) that maximises the
projection pursuit index. The discussion of existing optimisation
procedure will be discussed in the next section.

Guided tour creates visualisation for the projections found by
projection pursuit by constructing a tour path. An illustration modified
from \citep{buja2005computational} entails the geodesic interpolation
bewteen the plane generated by projection pursuit.

@@

As \citet{friedman1974projection} said ``\ldots{}, the technique use for
maximizing the (one- and two-dimensional) projection index strongly
influences both the statistical and the com- putational aspects of the
procedure.'' The quality of the optimisation procedure largely affect
the tour view and thus, the interesting projection one could possibly
observe. An ideal optimisation procedure needs to have following
characteristics:

\begin{itemize}
\item
  \emph{Being able to handle non-differentiable index function}: the
  index function could be noisy and non-differentible
\item
  \emph{Being able to optimise with constraints}: the projection matrix
  is restricted to an orthornormal matrix.
\item
  \emph{Being able to reveal both local and global maximum}: Although
  the primary interest is to find the global maximum, distinct local
  structures are also of our interest.
\end{itemize}

@@

\citet{posse1995projection} presented a random search algorithm that
samples new basis in the neighbourhood of the current basis. The
neighbourhood is defined via the radius of the p-dimenionsal sphere,
\(c\). The new basis is taken as the target basis if it has higher index
value, or the sampling continues. If no basis is found to have higher
index value after a certain humber of tries \(n\), the radius \(c\) is
halved. The algorithm stops when the maximum numbere of iteration is
attained or the radius \(c\) is less than a pre-determined number.
{[}Pursuit package uses this method and it works greate! But I don't
think we implement this - although don't think it is too hard to do
it{]}.

\citet{cook1995grand} explained the use of a gradient ascent
optimisation with the assumption that the index function is continuous
and differentiable. Since some indices could be non-differentiable, the
computation of derivative is replaced by a psudo-derivative of
evaluating five randomly generated directions in a tiny nearby
neighbourhood. Taking a step on the straight derivative direction has
been modified to maximise the projection pursuit index along the
geodesic direction.

@@

\emph{Think about how does your pacakge help people to understand
optimisation}

\begin{itemize}
\tightlist
\item
  diagnostic on stochastic optim
\item
  vis the prograssion of multi-parameter decision variable
\item
  understanding learning rate - neightbourhood parameter
\item
  understand where the local \& global maximum is found - trace plot -
  see if noisy function
\end{itemize}

@@

The psudo-code below illustrates the implementation of guided tour in
the tourr package. Given an projection pursuit index function and a
randomly generated projection basis (current basis), the optimisation
procedure produces a target basis inside \texttt{generator()} Both the
current basis and the target basis will be supplied to
\texttt{tour\_path()} to prepare information needed for constructing a
geodesic path. This information is then used to compute a series of
interpolating bases inside the \texttt{tour()} function. All the basis
will be sent to create animation for visualising the tour in the
\texttt{animate()} function.

@@

The graphical system in R is established based on the conception gramma
of graphic \citep{wickham2010layered}, where a graphic is defined using
stacked layers in a coordination system. A layer includes 1) the dataset
that powers the plot; 2) a geometric object that represents the visual
shape of the plot and 3) relevant statistical transformation if needed.
An important concept in the gramma of graphic is \emph{aesthetic
mapping}. Aesthetic mapping links the variable in a dataset to
information needed to produce a geometric object. For example, we map
one variable on the x-axis and another on the y-axis to create a
scatterplot. To create a boxplot, we first map one variable on the
x-axis and then map the five point summary of another variable on the
y-axis. This computation of five point summary from the origin variable
is statistical transformation. This definition of graphic through layers
provides advantages to produce complex plots since all the plots,
however complex, can be decomposed into basic geometric objects shaped
by the variable supplied.

@@

In the current implementation of the \texttt{tourr} package, while the
target basis generated by the projection pursuit can be accessed later
via \texttt{save\_history()}, interpolating bases and those randonly
nearby bases generated in the optimisation are not stored. This creates
difficulties for fully understand the behaviour of the optimisation and
interpolation of tour in complex scenario \textbf{{[}needa rephrase this
part{]}.}

Two set of simulated data are used in the demonstration of the
visualiation and diagnostics of the tour optimisation. A small dataset
consists of 1000 randomly simulated observations of five variables
(\texttt{x1}, \texttt{x2}, \texttt{x8}, \texttt{x9}, \texttt{x10}).
\texttt{x2} is the informative variable simulated from two bi-modal
normal distribution centered at -3 and 3 with variance being 1 and the
other four are simulated from \texttt{N(0,\ 1)}. The data has been
scaled to ensure \texttt{x2} has variance of 1.

@@

Once the dataset is sent to the tourr package, all the information
generated will be stored in a global structure. The global structure
consists of six columnes: \texttt{basis}, \texttt{index\_val},
\texttt{tries}, \texttt{info}, \texttt{loop}, \texttt{id} and captured
all the basis generated during whole tour process. The example below
presents the global object of a 1D projection of the small dataset with
geodesic seraching method.

@@

Given all the information of interest in a global object, the next thing
is to design its visual representation that can diagnose our algorithm.
In an iterative algorithm, one would be interested to know how one
parameter changes as the algorithm iterates. The parameter could be
could be the decision variable, the value of the optimisation function
or other parameter that facilitate the algorithm. In projectio pursuit
guided tour, apart from the decision variable projection basis, the
value of index function (\texttt{index\_val}), we are also interested to
explore the effect the different searching methods, the neighbourhood
parameter alpha, and the stage a particular observation is in
(\texttt{info}). These are the variables that will be mapped into the
diagnostic plot. The global object also has its time series nature since
the observations are recorded as the algorithm progresses and thus can't
be switch in rows. This time series structure is always hierachical and
nested since each row can be labelled with the smallest unit \texttt{id}
and up by the iterative structure of the algorithm. Take our example, in
the global object, each row has an \texttt{id} label which is the
smallest unit the observation is ordered. A larger ordering unit is
\texttt{tries} since it is updated everytime a new target basis is
found. A nested ordering unit is \texttt{loop}, which increases by one
as searching method iterates and starts over at a new \texttt{tries}.
These features explain the definition of the global object for
projection pursuit guided tour in Figure \ref{fig:glb-obj}.

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/points-id-1.pdf}
\caption{\label{points-id}this is a xxx}
\end{figure}

@@

Plotting the interpolating points as time series data allows us to
diagnose characterstics of different configurations and index functions.
Here we present two examples of using plots to diagnose the tour
algorithm and different index functions.

\emph{Example: Interruption} This examples uses \texttt{search\_better}
for a 2D projection on the larger dataset using the \texttt{holes}
index. As mentioned previously, the interpolation starts from the
current basis to the target basis, which has been found by the
projection pursuit algorithm to ahve a higher index value. After the
interpolation, the target basis will become the current basis and send
back to the projection pursuit algorithm to find the next target basis.
From figure \ref{fig:interruption}, it is possible that there are bases
with index value higher than the target basis on the interpolation path
and these bases could be used to search for new basis in the next
iteration.

Thus an interruption is constructed to accpet the interpolating bases up
to the one with the larget index value on the interpolation path, and
that basis is taken as the current basis for the next iteration. After
implementing this interruption, the tracing plot with the same
configuration is shown on the lower panel. We can observe that rather
than interpolating to the target basis at \texttt{id\ =\ 62}, the
interpolation stops before the index value starts to decrease at
\texttt{id\ =\ 60}. This implementation results in a higher index value
in the end with fewer steps.

@@

\emph{Example: Noisy index function} Add an example on noisy function

xxx

Currently, I have three things to put for the noisy index function.

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  interpolating plot finds that search\_geodesic is not doing a good job
  on optimising the noisy index; while search\_better is.
\item
  The interpolating plot for noisy index function is not smooth but the
  target basis is always increasing.
\item
  search\_better\_random sees to find both local and global maximum.
\end{enumerate}

Need to decise where to put this example. Do we wan to intoduce noisy
function at this stage or we put it here because they are insights draw
from the interpolating plots.

xxx

@@

\emph{Example: Polish} In principle, all the optimisation routines
should result in the same output on the same problem. Figure
\ref{fig:trace-compare} shows the interpolating plots for two different
searching methods: search\_geodesic and serach\_better on a 2D
projection problem for the larger dataset using the holes index. The two
methods reaches different ending value in the red dots, which is not
ideal. This motivates the creation of a polishing search that polishes
the ending basis and achieves unity on different methods.

\includegraphics{paper_files/figure-latex/trace-compare-1.pdf}

\texttt{search\_polish} takes the ending basis of a given search as the
current basis and uses a brutal-force approach to sample a larg number
of basis (\texttt{n\_sample}) in the neightbourhood, whose radius is
controlled by \texttt{polish\_alpha}. Among the \texttt{n\_sample}
basis, the one with the largest index value becomes the candidate. If
its index value of the candidate basis is larger than that of the
current basis, it becomes the current basis in the next iteration. If no
basis is found to have larger index value than the current basis, the
searching neighbourhood will be shrunk and the search continues. The
polishing search ends when one of the four stopping criteria is
satisfied:

@@

@@

Matrix parameter could also be interested to explore, for example, in
the tour, we are interested to explore the relative position of the
projection basis in the vector space. A projection basis is a
vector/matrix whose row number is the number of variable in the given
dataset. This imposes difficulties in visualisation since we are bounded
to preceive at most three dimensions. Thus, principal component analysis
is used to reduce the dimension of the projection basi and the first two
principal component are mapped to the x and y axis of the plot. Another
variable of interest could be mapped to the color aesthetics to see how
it changes as the projection basis changes in the projected 2D space.
{[}have a second read here{]}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/pca-1.pdf}
\caption{\label{pca}this is xxx}
\end{figure}

\emph{Example: understand the polishing alpha via mapping alpha to
color} \texttt{search\_polish} is a brutal-force algorithm that evaluate
1000 points in the neighbourhod at each loop and an appropriate inital
value in neighbourhood parameter alpha would avoid search on large
vector space and concentrate on the ending basis. In Figure, two
different initial alpha value is used in the polishing step. {[}some
more illustration of the comparison of the two polish alpha here{]}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_1d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_proj_pca}\NormalTok{(}\DataTypeTok{animate =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{col =}\NormalTok{ info)}
\end{Highlighting}
\end{Shaded}

>>>>

Guided tour is usually used in conjunction projection pursuit, a method
coined by \citet{friedman1974projection} to detect ``interesting''
low-dimension projection of multivariate data. A projection pursuit
requires the definition of a projection pursuit index function and an
optimisation routine. The projection pursuit index measures the
``interestingness'' of data defined as its departure from normality.
Numerous indices have been proposed in the literature, including
lengendre index \citep{friedman1974projection}, hermite index
\citep{hall1989polynomial}, natural hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}. An optimisation routine is required to
find the projection basis (thus projection) that maximises the
projection pursuit index. The discussion of existing optimisation
procedure will be discussed in the next section.

Guided tour creates visualisation for the projections found by
projection pursuit by constructing a tour path. An illustration modified
from \citep{buja2005computational} entails the geodesic interpolation
between the plane generated by projection pursuit.

@@

As \citet{friedman1974projection} said ``\ldots{}, the technique use for
maximizing the (one- and two-dimensional) projection index strongly
influences both the statistical and the computational aspects of the
procedure.'' The quality of the optimisation procedure largely affect
the tour view and thus, the interesting projection one could possibly
observe. An ideal optimisation procedure needs to have following
characteristics:

\begin{itemize}
\item
  \emph{Being able to handle non-differentiable index function}: the
  index function could be noisy and non-differentiable
\item
  \emph{Being able to optimise with constraints}: the projection matrix
  is restricted to an orthonormal matrix.
\item
  \emph{Being able to reveal both local and global maximum}: Although
  the primary interest is to find the global maximum, distinct local
  structures are also of our interest.
\end{itemize}

@@

\citet{posse1995projection} presented a random search algorithm that
samples new basis in the neighbourhood of the current basis. The
neighbourhood is defined via the radius of the p-dimensional sphere,
\(c\). The new basis is taken as the target basis if it has higher index
value, or the sampling continues. If no basis is found to have higher
index value after a certain number of tries \(n\), the radius \(c\) is
halved. The algorithm stops when the maximum number of iteration is
attained or the radius \(c\) is less than a pre-determined number.
{[}Pursuit package uses this method and it works great! But I don't
think we implement this - although don't think it is too hard to do
it{]}.

\citet{cook1995grand} explained the use of a gradient ascent
optimisation with the assumption that the index function is continuous
and differentiable. Since some indices could be non-differentiable, the
computation of derivative is replaced by a pseudo-derivative of
evaluating five randomly generated directions in a tiny nearby
neighbourhood. Taking a step on the straight derivative direction has
been modified to maximise the projection pursuit index along the
geodesic direction.

@@

\emph{Think about how does your package help people to understand
optimisation}

\begin{itemize}
\tightlist
\item
  diagnostic on stochastic optim
\item
  vis the progression of multi-parameter decision variable
\item
  understanding learning rate - neighbourhood parameter
\item
  understand where the local \& global maximum is found - trace plot -
  see if noisy function
\end{itemize}

@@

The pseudo-code below illustrates the implementation of guided tour in
the tourr package. Given an projection pursuit index function and a
randomly generated projection basis (current basis), the optimisation
procedure produces a target basis inside \texttt{generator()} Both the
current basis and the target basis will be supplied to
\texttt{tour\_path()} to prepare information needed for constructing a
geodesic path. This information is then used to compute a series of
interpolating bases inside the \texttt{tour()} function. All the basis
will be sent to create animation for visualising the tour in the
\texttt{animate()} function.

@@

The graphical system in R is established based on the conception grammar
of graphic \citep{wickham2010layered}, where a graphic is defined using
stacked layers in a coordination system. A layer includes 1) the dataset
that powers the plot; 2) a geometric object that represents the visual
shape of the plot and 3) relevant statistical transformation if needed.
An important concept in the grammar of graphic is \emph{aesthetic
mapping}. Aesthetic mapping links the variable in a dataset to
information needed to produce a geometric object. For example, we map
one variable on the x-axis and another on the y-axis to create a
scatterplot. To create a boxplot, we first map one variable on the
x-axis and then map the five point summary of another variable on the
y-axis. This computation of five point summary from the origin variable
is statistical transformation. This definition of graphic through layers
provides advantages to produce complex plots since all the plots,
however complex, can be decomposed into basic geometric objects shaped
by the variable supplied.

@@

In the current implementation of the \texttt{tourr} package, while the
target basis generated by the projection pursuit can be accessed later
via \texttt{save\_history()}, interpolating bases and those randomly
nearby bases generated in the optimisation are not stored. This creates
difficulties for fully understand the behaviour of the optimisation and
interpolation of tour in complex scenario \textbf{{[}need a rephrase
this part{]}.}

Two set of simulated data are used in the demonstration of the
visualisation and diagnostics of the tour optimisation. A small dataset
consists of 1000 randomly simulated observations of five variables
(\texttt{x1}, \texttt{x2}, \texttt{x8}, \texttt{x9}, \texttt{x10}).
\texttt{x2} is the informative variable simulated from two bi-modal
normal distribution centred at -3 and 3 with variance being 1 and the
other four are simulated from \texttt{N(0,\ 1)}. The data has been
scaled to ensure \texttt{x2} has variance of 1.

@@

Once the dataset is sent to the tourr package, all the information
generated will be stored in a global structure. The global structure
consists of six columns: \texttt{basis}, \texttt{index\_val},
\texttt{tries}, \texttt{info}, \texttt{loop}, \texttt{id} and captured
all the basis generated during whole tour process. The example below
presents the global object of a 1D projection of the small dataset with
geodesic searching method.

@@

Given all the information of interest in a global object, the next thing
is to design its visual representation that can diagnose our algorithm.
In an iterative algorithm, one would be interested to know how one
parameter changes as the algorithm iterates. The parameter could be
could be the decision variable, the value of the optimisation function
or other parameter that facilitate the algorithm. In projection pursuit
guided tour, apart from the decision variable projection basis, the
value of index function (\texttt{index\_val}), we are also interested to
explore the effect the different searching methods, the neighbourhood
parameter alpha, and the stage a particular observation is in
(\texttt{info}). These are the variables that will be mapped into the
diagnostic plot. The global object also has its time series nature since
the observations are recorded as the algorithm progresses and thus can't
be switch in rows. This time series structure is always hierarchical and
nested since each row can be labelled with the smallest unit \texttt{id}
and up by the iterative structure of the algorithm. Take our example, in
the global object, each row has an \texttt{id} label which is the
smallest unit the observation is ordered. A larger ordering unit is
\texttt{tries} since it is updated every time a new target basis is
found. A nested ordering unit is \texttt{loop}, which increases by one
as searching method iterates and starts over at a new \texttt{tries}.
These features explain the definition of the global object for
projection pursuit guided tour in Figure \ref{fig:glb-obj}.

@@

@@

Plotting the interpolating points as time series data allows us to
diagnose characteristics of different configurations and index
functions. Here we present two examples of using plots to diagnose the
tour algorithm and different index functions.

\emph{Example: Interruption} This examples uses \texttt{search\_better}
for a 2D projection on the larger dataset using the \texttt{holes}
index. As mentioned previously, the interpolation starts from the
current basis to the target basis, which has been found by the
projection pursuit algorithm to have a higher index value. After the
interpolation, the target basis will become the current basis and send
back to the projection pursuit algorithm to find the next target basis.
From figure \ref{fig:interruption}, it is possible that there are bases
with index value higher than the target basis on the interpolation path
and these bases could be used to search for new basis in the next
iteration.

Thus an interruption is constructed to accept the interpolating bases up
to the one with the larger index value on the interpolation path, and
that basis is taken as the current basis for the next iteration. After
implementing this interruption, the tracing plot with the same
configuration is shown on the lower panel. We can observe that rather
than interpolating to the target basis at \texttt{id\ =\ 62}, the
interpolation stops before the index value starts to decrease at
\texttt{id\ =\ 60}. This implementation results in a higher index value
in the end with fewer steps.

@@

\emph{Example: Noisy index function} The interpolation path of holes
index, as seen in Figure \ref{fig:interruption}, is smooth, while this
may not be the case for more complicated index function.
\texttt{kol\_cdf} index, an index function based on Kolmogorov test,
compares the difference between a projection matrix and a randomly
generated normal distribution based on cumulated distribution function
(CDF). Several visualisations below shows some characteristic of this
index function.

Figure \ref{fig:geodesic-better} compares the tracing plot of the
interpolating points for \texttt{search\_geodesic} and
\texttt{search\_better}. Rather than a smooth interpolation, the
interpolation path for \texttt{kol\_cdf} shows a zig-zag pattern.
Polishing step has done much more work to reach the final index value
for \texttt{search\_geodesic} than \texttt{search\_better} and this
indicates that noisy index's favour of a random search method than
ascent method.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/geodesic-better-1.pdf}
\caption{Comparison of two different searching methods: search\_geodesic
and search\_better on 1D projection problem for a noisy index: kol\_cdf.
The geodesic search rely heavily on the polishing step to find the final
index value while search better works well.}
\end{figure}

Moving from a 1D projection on a dataset with only one informative
variable, we now introduce another informative variable in the data and
remain 1D projection. In this problem, there are two local maximum being
0.17 when the projection matrix is \([0, 1, 0, 0, 0, 0]\) and 0.228 when
the projection matrix is \([0, 0, 1 ,0, 0, 0]\). As in Figure
\ref{fig:1d-2var-different-seeds}, using \texttt{search\_better} with
different seeds, both local maximum can be found. A simulated annealing
algorithm, \texttt{search\_better\_random} in Figure
\ref{fig:1d-2var-better-random}, can always find the global maximum at a
cost of a large number of \texttt{tries}.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/1d-2var-different-seeds-1.pdf}
\caption{The trace plot search better in a 1D projection problem with
two informative variables using different seeds (without polishing).
Since there are two informative variables, setting different value for
seed will lead search better to find either of the local maximum.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/1d-2var-better-random-1.pdf}
\caption{Using search better random for the problem above will result in
finding the global maximum but much larger number of iteration is
needed.}
\end{figure}

@@

\emph{Example: Polish} In principle, all the optimisation routines
should result in the same output on the same problem while this may not
be the case in real application. This motivates the creation of a
polishing search that polishes the ending basis and achieves unity on
different methods.

\texttt{search\_polish} takes the ending basis of a given search as the
current basis and uses a brutal-force approach to sample a large number
of basis (\texttt{n\_sample}) in the neighbourhood, whose radius is
controlled by \texttt{polish\_alpha}. Among the \texttt{n\_sample}
basis, the one with the largest index value becomes the candidate. If
its index value of the candidate basis is larger than that of the
current basis, it becomes the current basis in the next iteration. If no
basis is found to have larger index value than the current basis, the
searching neighbourhood will be shrunk and the search continues. The
polishing search ends when one of the four stopping criteria is
satisfied:

@@

\emph{Example: The neighbourhood parameter alpha} Add an example on
comparing the neighbourhood parameter in search\_better \&
search\_posse.

@@

Matrix parameter could also be interested to explore, for example, in
the tour, we are interested to explore the relative position of the
projection basis in the vector space. A projection basis is a
vector/matrix whose row number is the number of variable in the given
dataset. This imposes difficulties in visualisation since we are bounded
to perceive at most three dimensions. Thus, principal component analysis
is used to reduce the dimension of the projection basis and the first
two principal component are mapped to the x and y axis of the plot.
Another variable of interest could be mapped to the color aesthetics to
see how it changes as the projection basis changes in the projected 2D
space. {[}have a second read here{]}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/pca-1.pdf}
\caption{\label{pca}PCA plot of search geodesic Coloring by info allows
for better understanding of each stage in the geodesic search}
\end{figure}

\emph{Example: initial value for polishing alpha in search geodesic}
\texttt{search\_polish} is a brutal-force algorithm that evaluate 1000
points in the neighbourhood at each loop. Setting an appropriate initial
value for polish\_alpha would avoid wasting search on large vector space
that are not likely to produce higher index value. A default initial
value for polishing step is 0.5 and we are interested in whether this is
an appropriate initial value. The problem is a 1D projection of the
small dataset using \texttt{search\_geodesic} and followed by
\texttt{search\_polish}. Figure \ref{fig:polish-alpha} display all
projection bases on the first two principal components, colored by the
\texttt{polish\_alpha} parameter in the polishing step. Rather than
concentrating on the ending basis from \texttt{search\_geodesic} as what
polishing step is designed, it searches a much larger vector space that
are unnecessary. Thus a user-supplied smaller initial value for
\texttt{polish\_alpha} would be ideal.

On the right panel of Figure \ref{fig:polish-alpha-tracing}, the
\texttt{polish\_alpha} is initialised as the projection distance between
the last two target bases and we observe a concentrated searching space
near the ending basis. With the supplied initial value for
\texttt{polish\_alpha}, the algorithm reaches the same ending index
value with fewer iterations.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/polish-alpha-1.pdf}
\caption{PCA plot of two different polish alpha initialisations. A
default polish alpha = 0.5 searches a larger space that is unncessary
while a small customised initial value of polish alpha will search near
the ending basis.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/polish-alpha-tracing-1.pdf}
\caption{Comparing the trace of two different polish alpha
initialisations. Both intialisations reach the same ending index values}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_1d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_proj_pca}\NormalTok{(}\DataTypeTok{animate =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{col =}\NormalTok{ info) }\OperatorTok{+}\StringTok{ }
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \StringTok{"bottom"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
